### 2020-03-17 README.Rmd
pkgdown website should be working

# EpiCompare <img src="man/figures/logo.png" align="right" alt="" width="120" />

@@

>>>>

# EpiCompare <a href = "https://skgallagher.github.io/EpiCompare/"><img src="man/figures/logo.png" align="right" alt="" width="120" /></a>

@@

## Documentation

Please see our website at [https://skgallagher.github.io/EpiCompare/](https://skgallagher.github.io/EpiCompare/).
